Modular Synthesis of Verified Verifiers of Computation with STV Algorithms

### 2019-03-15 paper/paper.tex
references matched with the IEEE standards

\begin{thebibliography}{00}
\bibitem{act}
ACT Electoral Commission, \url{www.elections.act.gov.au/elections_and_voting} 
\bibitem{MBlo}
M.L. Blom, P. J. Stuckey, V. J. Teague, Computing the Margin of Victory in Preferential Parliamentary Elections, E-Vote-ID, 2018, pp.1--16
\bibitem{cade}
CADE: The Single Transferable Vote, \url{http://www.cadeinc.org//bylaws} 
\bibitem{cake} 
CakeML: A Verified Implementation of ML, \url{https://cakeml.org/}
\bibitem{DBLP:conf/voteid/DawsonGM15}
J.E. Dawson, R. Gor{\'{e}}, T. Meumann, Machine-checked Reasoning about
  Complex Voting Schemes Using Higher-order Logic, EVote-ID 2015, pp.142--158
\bibitem{Dolphin}
The Delphine Project, \url{http://delphin.poswolsky.com/home}
\bibitem{DeYoung:2012:LLV}
H. DeYoung, C. Sch{\"{u}}rmann, Linear Logical Voting Protocols, VoteID 2011, LNCS Springer, pp. 53--70
\bibitem{Droop:1881:MER}
H.R. Droop, On Methods of Electing Representatives. J. of the Statistical
  Society of London  44(2), 1881, pp.141--202
\bibitem{DFar}
D.M. Farrell, Electoral Systems: A Comparative Introduction, 2nd ed., New York: Palgrave Macmillan, 2011
\bibitem{Ghale:2017:FVS}
M.K. Ghale, R. Gor{\'{e}}, D. Pattinson, A Formally Verified Single Transferable Voting Scheme with Fractional Values, E-Vote-ID 2017, pp.163--182
\bibitem{Ghale2018}
M.K. Ghale, R. Gor{\'{e}}, D. Pattinson, M. Tiwari,
 Modular Formalisation and Verification of STV Algorithms, E-Vote-ID 2018, pp.51--66
\bibitem{GhaleVSTTE}
M.K. Ghale, D. Pattinson, R. Kumar, M. Norrish, Verified Certificate Checking for Counting Votes, VSTTE 2018, pp.69--87
\bibitem{DBLP:journals/apal/Girard93}
J. Girard, On the Unity of Logic. Ann. Pure Appl. Logic  59(3), 1993, pp.201--217
\bibitem{cakeTrans}
S. Ho, O. Abrahamsson, R. Kumar, M. O. Myreen, Y. K. Tan,  Michael Norrish, Proof-Producing Synthesis of CakeML with {I/O} and Local State from Monadic HOL Functions, Proc. 9th Conf. IJCAR 2018, pp. 646--662
\bibitem{hol}
HOL Interactive Theorem Prover, https://hol-theorem-prover.org/
\bibitem{CertAlg}
R.M. Mcconnell, K. Mehlhorn, S. N\"{a}her, P. Schweitzer, Survey: Certifying Algorithms, J. Comput. Sci. Rev., vol5(2), 2011, pp.119--161
%\bibitem{cakeTrans}
%M. O. Myreen, S. Owens, Proof-producing Translation of Higher-order Logic into Pure and Stateful ML, J. Funct. Program. vol. 24, no. 2-3, pp. 284--315, 2014
\bibitem{DBLP:conf/ausai/PattinsonS15}
D. Pattinson, C. Sch{\"{u}}rmann, Vote Counting as Mathematical Proof, 28th Australasian Joint
  Conference 2015, pp.464--475
\bibitem{DBLP:conf/itp/PattinsonT17}
D. Pattinson, M. Tiwari, Schulze Voting as Evidence Carrying Computation, ITP 2017, pp.410--426
\bibitem{vic}
The Parliament of Victoria: Electoral Act 2002
\bibitem{DBLP:conf/acsw/VerityP17}
F. Verity, D. Pattinson, Formally Verified Invariants of Vote Counting Schemes, ACSW 2017, pp.1--10 
\bibitem{CakeComp}
Tan K. Yong, M. O. Myreen, R. Kumar, A. C. J. Fox, S. Owens, M. Norrish, A New Verified Compiler Backend for CakeML, Proc. 21st ACM SIGPLAN, ICFP 2016, pp.60--73
%\bibitem{cake1}
%R. Kumar, M.O. Myreen, M. Norrish, S. Owens, CakeML: A Verified Implementation of ML, POPL, 2014
%\bibitem{cake2}
%M.O. Myreen, O. Scott: 
%Proof-producing Translation of Higher-order Logic into Pure and Stateful ML. J. Funct. Program., 2014, pp.284-315
%\bibitem{hol}
%K. Slind, M. Norrish, A Brief Overview of HOL4, Theorem Proving in Higher Order Logics, Springer, 2008
\end{thebibliography}
\end{document}
% vim: ft=tex

>>>>

\begin{thebibliography}{00}
\bibitem{act}
ACT Electoral Commission, \url{www.elections.act.gov.au/elections_and_voting} 
\bibitem{MBlo}
M. L. Blom, P. J. Stuckey, V. J. Teague, ``Computing the Margin of Victory in Preferential Parliamentary Elections'' in 3ed Intern. Conf. Proc., Bregenz, Austria, 2018, pp. 1--16
%\bibitem{MBlo}
%M.L. Blom, P. J. Stuckey, V. J. Teague, Computing the Margin of Victory in Preferential Parliamentary Elections, E-Vote-ID, 2018, pp.1--16
\bibitem{cade}
CADE: The Single Transferable Vote, \url{http://www.cadeinc.org//bylaws} 
\bibitem{cake} 
CakeML: A Verified Implementation of ML, \url{https://cakeml.org/}
\bibitem{DBLP:conf/voteid/DawsonGM15}
J.E. Dawson, R. Gor{\'{e}}, T. ``Meumann, Machine-checked Reasoning about Complex Voting Schemes Using Higher-order Logic'' in 5th Intern. Conf. VoteID, Bern, Switzerland, 2015, pp.142--158
\bibitem{Dolphin}
The Delphine Project, \url{http://delphin.poswolsky.com/home}
\bibitem{DeYoung:2012:LLV}
H. DeYoung, C. Sch{\"{u}}rmann, ``Linear Logical Voting Protocols'' in 3ed Intern. Conf. VoteID, Tallin, Estonia, 2011, pp. 53--70
\bibitem{Droop:1881:MER}
H.R. Droop, ``On Methods of Electing Representatives''. J. of the Statistical
  Society of London  44(2), 1881, pp.141--202
\bibitem{DFar}
D.M. Farrell, ``Electoral Systems: A Comparative Introduction'', 2nd ed., New York: Palgrave Macmillan, 2011
\bibitem{Ghale:2017:FVS}
M.K. Ghale, R. Gor{\'{e}}, D. Pattinson, ``A Formally Verified Single Transferable Voting Scheme with Fractional Values'' in 2en Intern. Join Conf. E-Vote-ID, Bregenz, Austria, 2017, pp.163--182
\bibitem{Ghale2018}
M.K. Ghale, R. Gor{\'{e}}, D. Pattinson, M. Tiwari,
 ``Modular Formalisation and Verification of STV Algorithms'' in 3ed Intern. Joint Conf. E-Vote-ID, Bregenz, Austria, 2018, pp.51--66
\bibitem{GhaleVSTTE}
M.K. Ghale, D. Pattinson, R. Kumar, M. Norrish, ``Verified Certificate Checking for Counting Votes'' in 10th Intern. Conf. VSTTE, Oxford, UK, 2018, pp.69--87
\bibitem{DBLP:journals/apal/Girard93}
J. Girard, ``On the Unity of Logic'', Ann. Pure Appl. Logic  59(3), 1993, pp.201--217
\bibitem{cakeTrans}
S. Ho, O. Abrahamsson, R. Kumar, M. O. Myreen, Y. K. Tan,  Michael Norrish, ``Proof-Producing Synthesis of CakeML with I/O and Local State from Monadic HOL Functions'' in 9th  Intern. Joint Conf. IJCAR, Oxford, UK, 2018, pp. 646--662
\bibitem{hol}
HOL Interactive Theorem Prover, https://hol-theorem-prover.org/
\bibitem{CertAlg}
R.M. Mcconnell, K. Mehlhorn, S. N\"{a}her, P. Schweitzer, ``Survey: Certifying Algorithms'' J. Comput. Sci. Rev., vol5(2), 2011, pp.119--161
%\bibitem{cakeTrans}
%M. O. Myreen, S. Owens, Proof-producing Translation of Higher-order Logic into Pure and Stateful ML, J. Funct. Program. vol. 24, no. 2-3, pp. 284--315, 2014
\bibitem{DBLP:conf/ausai/PattinsonS15}
D. Pattinson, C. Sch{\"{u}}rmann, ``Vote Counting as Mathematical Proof'' in 28th Australasian Joint
  Conf., Canberra, Australia, 2015, pp.464--475
\bibitem{DBLP:conf/itp/PattinsonT17}
D. Pattinson, M. Tiwari, ``Schulze Voting as Evidence Carrying Computation'' in 8th Intern. Con. ITP, Bras{\'i}lia, Brazil, 2017, pp.410--426
\bibitem{vic}
The Parliament of Victoria: Electoral Act 2002
\bibitem{DBLP:conf/acsw/VerityP17}
F. Verity, D. Pattinson, ``Formally Verified Invariants of Vote Counting Schemes'' in ACSW, Geelong, Australia, 2017, pp.1--10 
\bibitem{CakeComp}
Tan K. Yong, M. O. Myreen, R. Kumar, A. C. J. Fox, S. Owens, M. Norrish, ``A New Verified Compiler Backend for CakeML'' in 21st ACM SIGPLAN, ICFP, Nara, Japan, 2016, pp.60--73
%\bibitem{cake1}
%R. Kumar, M.O. Myreen, M. Norrish, S. Owens, CakeML: A Verified Implementation of ML, POPL, 2014
%\bibitem{cake2}
%M.O. Myreen, O. Scott: 
%Proof-producing Translation of Higher-order Logic into Pure and Stateful ML. J. Funct. Program., 2014, pp.284-315
%\bibitem{hol}
%K. Slind, M. Norrish, A Brief Overview of HOL4, Theorem Proving in Higher Order Logics, Springer, 2008
\end{thebibliography}
\end{document}
% vim: ft=tex
